\documentclass[11pt]{article}

% Internet-Draft identity (a proposal is a named draft, never a self-assigned RFC number)
\newcommand{\jobIDname}{draft-paruk-dmtap-00}
\newcommand{\jobIDdate}{July 2026}
\newcommand{\jobIDexpiry}{January 2027}
\newcommand{\jobIDstatus}{Experimental}

\input{preamble}

\begin{document}
\sloppy

% ===========================================================================
% Front matter — styled like an Internet-Draft cover
% ===========================================================================
\thispagestyle{empty}
\begin{flushleft}
{\small\color{faintGray}
Network Working Group\hfill I.\ Paruk\\
Internet-Draft\hfill Envoir\\
Intended status: \jobIDstatus\hfill \jobIDdate\\
Expires: \jobIDexpiry\\[-0.3ex]
}
\end{flushleft}

\vspace{2.2cm}
\begin{center}
{\LARGE\bfseries\color{inkGray} Decentralized Message Transfer \&\\[2pt] Access Protocol (DMTAP)}\\[6pt]
{\large\color{envoirViolet}\texttt{\jobIDname}}\\[10pt]
{\color{faintGray}\rule{0.5\linewidth}{0.6pt}}
\end{center}

\vspace{0.8cm}
\subsection*{Abstract}
DMTAP is an open protocol for sovereign, metadata-private communication --- mail,
chat, and files --- and decentralized identity/login, over a peer-to-peer mesh, with
an optional bridge to legacy email. It unifies message \emph{transfer} (the role of
SMTP) and message \emph{access} (the role of IMAP) into one decentralized, encrypted
protocol, and extends the same keypair identity into decentralized web login. A user's
identity is a keypair; a human name (an 8-word key-derived name, an @handle, or a
domain) is a replaceable pointer to it. Content, authenticity, and the social graph are
protected: messages are end-to-end encrypted and signed, and who-talks-to-whom is hidden
from a global passive observer. DMTAP composes existing standards (MLS, HPKE, JMAP,
libp2p, DNS, key transparency, Privacy Pass, WebAuthn, OAuth, DID); the novelty is the
composition and transport, not new cryptography.

\subsection*{Status of This Memo}
{\small This Internet-Draft is submitted in full conformance with the provisions of an
open, royalty-free specification. Internet-Drafts are working documents; this document
is a \jobIDstatus{} proposal and is \emph{not} an RFC --- an RFC number is assigned only
upon publication by the relevant standards body. It is valid for a maximum of six months
and may be updated, replaced, or obsoleted by other documents at any time. It is
inappropriate to use this document as reference material or to cite it other than as
``work in progress.'' This draft will expire on \jobIDexpiry.}

\subsection*{Requirements Language}
{\small The key words \textbf{MUST}, \textbf{MUST NOT}, \textbf{REQUIRED},
\textbf{SHALL}, \textbf{SHALL NOT}, \textbf{SHOULD}, \textbf{SHOULD NOT},
\textbf{RECOMMENDED}, \textbf{MAY}, and \textbf{OPTIONAL} in this document are to be
interpreted as described in RFC~2119 and RFC~8174 when, and only when, they appear in
all capitals.}

\subsection*{Copyright Notice}
{\small Copyright \textcopyright{} 2026 Imran Paruk and the DMTAP contributors. This
specification is licensed under Creative Commons Attribution 4.0 International
(CC~BY~4.0); reference implementations are licensed separately under MIT.}

\vfill
\begin{center}\small\color{faintGray}
Reference implementation: \emph{Envoir} (MIT). \quad Message object: \emph{MOTE}.
\end{center}
\clearpage

% ===========================================================================
% Table of contents
% ===========================================================================
{\hypersetup{linkcolor=inkGray}
\renewcommand{\contentsname}{\color{inkGray}Table of Contents}
\tableofcontents}
\clearpage

% ===========================================================================
% Body — generated section files (pandoc-converted from the spec markdown)
% ===========================================================================
\input{body/00-overview}
\input{body/01-identity}
\input{body/02-mote}
\input{body/03-naming}
\input{body/04-transport}
\input{body/05-messaging}
\input{body/06-privacy}
\input{body/07-gateway}
\input{body/08-clients}
\input{body/09-anti-abuse}
\input{body/10-conformance}
\input{body/11-grounding-and-references}
\input{body/12-operators}
\input{body/13-identity-auth}
\input{body/14-scaling}
\input{body/15-references}
\input{body/16-parameters}

\vfill
\begin{center}\small\color{faintGray}\jobIDname\ --- Expires \jobIDexpiry\end{center}
\end{document}
